Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-14 chi2012.tex
prestudy
Fix apostrophes

\subsection{PS.1 - Understanding Data Diversity in Everyday Tasks}
Our pre-study investigated the types of tasks people perform online that required heterogeneous data sources, and which tools they would use to organise a large social event involving 15 or more people.  We interviewed 8 participants, using a general interview guide approach based loosely on a set of questions (see Appendix ?).  This approach allowed both the participant and interviewer a degree of freedom in conversation and each interview could adapt to the participantÕs experiences, while collecting the same general areas of information.  Each interview was recorded and notes taken, the interviewer was trained so that they were knowledgeable about the importance of the study and to minimise bias.

@@

Most people felt that being assertive and posting their decisions about the date and time on Facebook meant that organising events were more successful than trying to gather a consensus.  They expected that their friends would voice any objections if they could not attend or like the restaurant or activity selected.   They selected venues, locations, restaurants and activities based on their own knowledge, friendÕs recommendations, Google maps, reviews through Googling and review sites such as tripadvisor.  People stated that the cost, price and easy to get to locations were the most important factors when choosing a venue.  They considered how to get there and looked up train or bus times on the Web.  One participant organised carpools informally and at last minute via Facebook or text messages.

When organising an event the weather was not that important because it they did not trust its accuracy for events plan further in the future than one week.  Also, their friendÕs preferences in price and food choices were not a priority; they would try to be inclusive but only if it meant small changes to the plan.  Choosing food and timings were often made on-the-fly, by either with the use of mobile applications or by walking past a location.

@@

\subsection{Participants}
We recruited 20 participants (10 female) from the University of SouthamptonÕs international student mailing list.  All of the participants spoke English, and for 12 of them, English was not their first language, however they had all passed the university English proficiency test.  Predominately the participants were studying various levels of Computer Science, and 5 of which studied other subjects.  All of the participants had previously encountered tasks requiring them to use and evaluate data from multiple websites.

@@

\subsection{Data Collection}
Each study was overseen by a facilitator and an observer:  the role of the facilitator was to explain the studyÕs protocol to the participant and to answer any questions; and the role of the observer was to observe without interacting with the user, and to take notes.  During the lab study, we recorded the audio and the participantÕs actions on screen. We asked the participants to speak out loud their thought process and what they were looking at, so that we could evaluate their reasoning behind their processes.

The studies lasted 40 minutes, on average.  Both the facilitator and observer were trained on the purpose of the study, their role and how they could and couldnÕt influence the study.  The studies were run over 4 days.  At the end of each day the facilitators and observers met to discuss the studiesÕ data and to revisit protocols, if necessary.

@@

During the data collection we collated a spreadsheet summarising the participantÕs gender, typical daily computer usage, the tasks allocated and basic actions performed during the task.  After we had collected the studyÕs data, we performed our data analysis.

@@

%What we found 
%
%What we didnÕt find (evidence for)
%
%What we might look at next -- follow-on work
%		We focused on terminological heterogeneity -- didnÕt address structural heterogeneity, semantic heterogeneity
%		We focused on finite (small) sets Streaming data (how do select future data --) 
%		Scale - small data, what are the facilites required for large data
%		Collaborative - how might interaction support multiple users collaborating?
%
%Limitations found from study... what is the take away from the limitations

>>>>

\subsection{PS.1 - Understanding Data Diversity in Everyday Tasks}
Our pre-study investigated the types of tasks people perform online that required heterogeneous data sources, and which tools they would use to organise a large social event involving 15 or more people.  We interviewed 8 participants, using a general interview guide approach based loosely on a set of questions (see Appendix ?).  This approach allowed both the participant and interviewer a degree of freedom in conversation and each interview could adapt to the participant's experiences, while collecting the same general areas of information.  Each interview was recorded and notes taken, the interviewer was trained so that they were knowledgeable about the importance of the study and to minimise bias.

@@

Most people felt that being assertive and posting their decisions about the date and time on Facebook meant that organising events were more successful than trying to gather a consensus.  They expected that their friends would voice any objections if they could not attend or like the restaurant or activity selected.   They selected venues, locations, restaurants and activities based on their own knowledge, friend's recommendations, Google maps, reviews through Googling and review sites such as tripadvisor.  People stated that the cost, price and easy to get to locations were the most important factors when choosing a venue.  They considered how to get there and looked up train or bus times on the Web.  One participant organised carpools informally and at last minute via Facebook or text messages.

When organising an event the weather was not that important because it they did not trust its accuracy for events plan further in the future than one week.  Also, their friend's preferences in price and food choices were not a priority; they would try to be inclusive but only if it meant small changes to the plan.  Choosing food and timings were often made on-the-fly, by either with the use of mobile applications or by walking past a location.

@@

\subsection{Participants}
We recruited 20 participants (10 female) from the University of Southampton's international student mailing list.  All of the participants spoke English, and for 12 of them, English was not their first language, however they had all passed the university English proficiency test.  Predominately the participants were studying various levels of Computer Science, and 5 of which studied other subjects.  All of the participants had previously encountered tasks requiring them to use and evaluate data from multiple websites.

@@

\subsection{Data Collection}
Each study was overseen by a facilitator and an observer:  the role of the facilitator was to explain the study's protocol to the participant and to answer any questions; and the role of the observer was to observe without interacting with the user, and to take notes.  During the lab study, we recorded the audio and the participant's actions on screen. We asked the participants to speak out loud their thought process and what they were looking at, so that we could evaluate their reasoning behind their processes.

The studies lasted 40 minutes, on average.  Both the facilitator and observer were trained on the purpose of the study, their role and how they could and couldn't influence the study.  The studies were run over 4 days.  At the end of each day the facilitators and observers met to discuss the studies' data and to revisit protocols, if necessary.

@@

During the data collection we collated a spreadsheet summarising the participant's gender, typical daily computer usage, the tasks allocated and basic actions performed during the task.  After we had collected the study's data, we performed our data analysis.

@@

%What we found 
%
%What we didn't find (evidence for)
%
%What we might look at next -- follow-on work
%		We focused on terminological heterogeneity -- didn't address structural heterogeneity, semantic heterogeneity
%		We focused on finite (small) sets Streaming data (how do select future data --) 
%		Scale - small data, what are the facilites required for large data
%		Collaborative - how might interaction support multiple users collaborating?
%
%Limitations found from study... what is the take away from the limitations
